Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-11 paper/structureScene.tex
up
update EMD description

with $c_N$ the $N$'th nearest neihgbor of the centroid $c_i$.

@@

This section present evaluation results for the ASS settings. $p@k$ for different settings are showed in the Figures \ref{fig:ASS_1} and \ref{fig:ASS_2}.

@@

For both the MFCCs and the time-scattering, \emph{ob-c} and \emph{ob-w} outperform \emph{ei}, thus confirming the benefits of using an object-based representation to refine the similarity measures between the scenes. However, it is worth noticing that \emph{ob-a} perform equivalently to \emph{ei}, which shows that the discriminant information is not carried by all the centroids. To take advantage of an object-based representation, a selection step has to be run on the representatives of the scenes.

@@

Outcomes for time-scattering with and without log compression are showed in Figure~\ref{fig:ASS_2}. It can be seen that the log compression strongly improves the results, specially for the \emph{ob} approaches, which perform lesser than \emph{ei} without the log compression. \gl{une idée du pourquoi ?}

>>>>

with $c_N$ the $N$'th nearest neihgbor of the centroid $c_i$, and $\parallel \bullet \parallel$ the euclidean norm.

@@

This section present evaluation results for the ASS settings. The $p@k$ for different settings are showed in the Figures~\ref{fig:ASS_1} and \ref{fig:ASS_2}.

@@

For both MFCCs and time-scattering, \emph{ob-c} and \emph{ob-w} outperform \emph{ei}, thus confirming the benefits of using an object-based representation to refine the similarity measures between the scenes. However, it is worth noticing that \emph{ob-a} perform equivalently to \emph{ei}, which shows that the discriminant information is not carried by all the centroids. To take advantage of an object-based representation, a selection step has to be run on the representatives of the scenes.

@@

Outcomes for the time-scattering with and without log compression are showed in Figure~\ref{fig:ASS_2}. It can be seen that the log compression strongly improves the results, specially for the \emph{ob} approaches, which perform lesser than \emph{ei} without the log compression. \gl{une idée du pourquoi ?}
